Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-03-19 docs/manuscript/main.tex
figure04 harmonised and updated

\subsubsection*{Uniform Time-Delay Embedding}
Using the overall embedding parameters ($\overline{m_0}=6$, $\overline{\tau_0}=8$), 
the first three axis of the rotated Principal Components Analysis (PCA) 
are shown for the reconstructed state spaces of horizontal (figures~\ref{fig:rsss}(A)) 
and vertical (figures~\ref{fig:rsss}(B)) arm movements. 
While visual inspection of these figures 
suggests differences in the trajectories of the reconstructed state spaces, 
we require an objective quantification to determine the extent of the differences.  
One approach could be use Euclidean distances from the origin for points in these 
trajectories, but this proved inconclusive and was not able to capture 
the dynamics of the trajectories. Consequently, we applied 
Recurrence Plots and Recurrence Quantification Analysis.
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rss/versions/drawing-v00.pdf}
\caption{
	{\bf RSSs for horizontal and vertical arm movements.}
	Reconstructed state spaces for time series for p01 of Figure \ref{fig02}C.
	Reconstructed state spaces were computed with 
	embedding parameters 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$
	for (A) horizontal and (B) vertical arm movements.
	Code and data to reproduce the figure is available in \cite{srep2021}.	
        }
    \label{fig:rsss}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------

>>>>

\subsubsection*{Uniform Time-Delay Embedding}
Using the overall embedding parameters ($\overline{m_0}=6$, $\overline{\tau_0}=8$), 
the first three axis of the rotated Principal Components Analysis (PCA) 
are shown for the reconstructed state spaces of horizontal (figures~\ref{fig04}(A))
and vertical (figures~\ref{fig04}(B)) arm movements.
While visual inspection of these figures 
suggests differences in the trajectories of the reconstructed state spaces, 
we require an objective quantification to determine the extent of the differences.  
One approach could be use Euclidean distances from the origin for points in these 
trajectories, but this proved inconclusive and was not able to capture 
the dynamics of the trajectories. Consequently, we applied 
Recurrence Plots and Recurrence Quantification Analysis.
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rss/versions/drawing-v01}
\caption{
	{\bf RSSs for horizontal and vertical arm movements.}
	Reconstructed state spaces for time series for p01 of Figure \ref{fig02}C.
	Reconstructed state spaces were computed with 
	embedding parameters 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$
	for (A) horizontal and (B) vertical arm movements.
	Code and data to reproduce the figure is available in \cite{srep2021}.	
        }
    \label{fig04}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------
